%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

I want to thank the following people for helping me with the development of this work:\\

To Professor Giambattista Gruosso, for giving me the opportunity to develop such an interesting thesis project and for his guidance through the research method for this kind of projects, which is as valuable as the knowledge I gained regarding the topic developed in this work.

To Professor Luca Bascetta, for giving me advice and material regarding the research and implementation of the motor control theory and the work already developed regarding this project.

To Professor Luigi Piegari, for his support and advice on the final tests and the examination of the thesis.

To Professor Federico Terraneo, for his support and interest on the implementation of Miosix in this project, and to the Skyward Experimental Rocketry team, for their help with the CAN bus driver.

To Marco Bauer, for his support in the aspects related to the mechanics of the project and also for providing me with information of the work already developed.

To Giulio Fontana, for his support and advice regarding the manufacture of the systems developed for this work while working in the AIRLab.

To Professor Luigi Colombo for providing me documentation regarding the thermal management proposal developed in this work.

To Stefano Bianchi for helping with the fine details of the tunning of the controllers and with the development of the tests.

To Milica Jovanovic for helping me with the documentation of the software architecture and with the flowcharts.\\

%I also want to thank all the people with whom I've been sharing my time while studying in Milano these almost three years: my flatmate Simone Fabbiano, my close friends Ludwig, Carlos, Omar, Gerardo, Aldo, Guillermo, Natalia, Brenda, Rosario, Emilia, Felipe, Alessandro, Adrià, Mònica, all the Osber basketball team, my friends from ESN Politecnico di Milano and the guys from BEST Mostar and from the Spring Course 2017.

\endgroup